Identification of protoneutron star g-modes in gravitational-wave data \pcd{[PCD: alt. title]Inference of proto-neutron star properties from gravitational wave data in core-collapse supernovae.}

### 2020-09-15 methods.tex
Comments on section III

\section{Methods description}
\label{methods}

@@

Using 25 spherically symetric (1D) simulations obtained with the {\sc AENUS-ALCAR }code \citep{Just_et_al__2015__mnras__Anewmultidimensionalenergy-dependenttwo-momenttransportcodeforneutrino-hydrodynamics} and the
{\sc CoCoNuT} \citep{Cerda-Duran__2008__AA__GRMHD-code} code, we parametrize the ratio with a cubic polynomial
regression with heteroscedastic errors
%Here we are using the data from \textcolor{red}{only {\sc AENUS-ALCAR} or both?, maybe colour-code the two groups of data points } to fit a cubic polyn

@@

\begin{figure}
 \centering
 \includegraphics[width=0.5\textwidth]{plots/model}
 \caption{Ratio $M_{\rm PNS}/R_{\rm PNS}^2$ from 25 1D simulations {\sc AENUS-ALCAR} (red) and {\sc CoCoNuT} (green) code. The solid line is the maximum likelihood estimate of heteroscedastic cubic model with 95\% confidence bands (dashed lines) considering the {\sc AENUS-ALCAR} data points.} \label{fig:LMVAR}
\end{figure}

To develop the method we considered the gravitational wave signal
{\texttt s20S} described in Section \ref{sec:simulations}, originally
sampled at 16384 Hz but resampled at 4096 Hz.
A spectrogram of this signal is shown in Figure \ref{fig:spectrogram} based on
autoregressive estimates of the local spectra for successive time intervals of 
\textcolor{red}{length 200} with a \textcolor{red}{ 90\%} overlap.
The dominant emission mode corresponds to the PNS oscillation $\mbox{}^2 g_2$-mode. We have
developed a time-frequency method to track the ridge $m(t)$ in the spectrogram,
taking into account that it is monotonically increasing as time goes,
a property of the $\mbox{}^2 g_2$-mode.
Starting from either the left- or right-most column of the time-frequency matrix
we identify and trace the sequence of amplitude peaks within a certain frequency
band given the monotonicity constraint. Appendix \ref{app:gmode} is providing more
details on the reconstruction of the $g$ mode ridge.

@@

We collect the instantaneous frequency $f(t_i)$ corresponding to the ridge $m(t_i)$ for
the midpoint $t_i$ of each local time interval of the spectrogram and interpolating $f(t)$
for values in between the $t_i$. We then use equation \eqref{eq:model1} to obtain
estimates of the time evolution of the ratio together with 95\% confidence intervals.
An exemple is given in Figure \ref{fig:ratio} where the red points are the point estimates and
the grey bands represent 95\% confidence bands. Ratio values
computed using the mass and radius values obtained from the simulation code are shown in black.

@@

In this case, for a GW signal without any noise, the coverage of our 95\% confidence band is 94\%.
In the next section we investigate the performance of reconstruction of $r(t)$ when the gravitational wave
signal is embedded in noise.

>>>>

% !TEX root = ccsn.tex
\section{Methods description}
\label{methods}

@@

\pcd{To build the model of the ratio $r$ as a function of the frequency $f$ we use the 
spherically symetric (1D) simulations of the {\it model set}. Figure~\ref{fig:LMVAR}
shows the data for the $25$ numerical simulations. As identified by \cite{Torres:2019b}, the only systematic
deviation from a single universal relation is the numerical code used in the simulations. 
To avoid any systematic effect, we only use to build our model the $18$ simulations performed with the ALCAR-AENUS
code, which is the same code that was used in our test set. The consequences of this choice are discussed in the
conclusions. Using this data, we} parametrize the ratio with a cubic polynomial
regression with heteroscedastic errors
%Here we are using the data from \textcolor{red}{only {\sc AENUS-ALCAR} or both?, maybe colour-code the two groups of data points } to fit a cubic polyn

@@

\begin{figure}
 \centering
 \includegraphics[width=0.5\textwidth]{plots/model}
 \caption{Ratio $M_{\rm PNS}/R_{\rm PNS}^2$ from 25 1D simulations {\sc AENUS-ALCAR} (red) and {\sc CoCoNuT} (green) code. The solid line is the maximum likelihood estimate of heteroscedastic cubic model with 95\% confidence bands (dashed lines) considering \pcd{only} the  {\sc AENUS-ALCAR} data points \pcd{($18$ simulations)}.} \label{fig:LMVAR}
\end{figure}

\pcd{We use this model to infer the properties of the simulations in the 
{\it test set} described in in Section \ref{sec:simulations}.}
To develop \pcd{and describe} the method we \pcd{\sout{considered} focus on} the gravitational wave signal
\pcd{of} {\texttt s20S}, originally
sampled at 16384 Hz but resampled at 4096 Hz.
A spectrogram of this signal is shown in Figure \ref{fig:spectrogram} based on
autoregressive estimates \pcd{[CITATION?]}of the local spectra for successive time intervals of 
\textcolor{red}{length 200} with a \textcolor{red}{ 90\%} overlap.
The dominant emission mode corresponds to the PNS oscillation $\mbox{}^2 g_2$-mode. We have
developed a time-frequency method to track the ridge $m(t)$ in the spectrogram,
taking into account that it is monotonically increasing as time goes. 
\pcd{This is a property of the $\mbox{}^2 g_2$-mode, the frequency of which  
increases as the object becomes more massive and compact}.
Starting from either the left- or right-most column of the time-frequency matrix
we identify and trace the sequence of amplitude peaks within a certain frequency
band given the monotonicity constraint. Appendix \ref{app:gmode} is providing more
details on the reconstruction of the $g$ mode ridge.

@@

We collect the instantaneous frequency $f(t_i)$ corresponding to the ridge $m(t_i)$ for
the midpoint $t_i$ of each local time interval of the spectrogram and interpolating $f(t)$
for values in between the $t_i$. We then use \pcd{our model given by Eq.~}
\eqref{eq:model1} to obtain
estimates of the time evolution of the ratio together with 95\% confidence intervals.
An exemple is given in Figure \ref{fig:ratio} where the red points are the point estimates and
the grey bands represent 95\% confidence bands. Ratio values
computed using the mass and radius values obtained from the simulation code \pcd{(true values)} are shown in black.

@@

In this case, for a GW signal without any noise, the coverage of our 95\% confidence band is 94\% \pcd{of the true values}.
In the next section we investigate the performance of \pcd{the} reconstruction of $r(t)$ when the gravitational wave
signal is embedded in noise.

### 2020-09-15 simulations.tex
Comments on section III

{For the {\it model set}, we use the $25$ spherically symmetric (1D) simulations of \citep{Torres:2019a}
including progenitors with zero-age main sequence (ZAMS) masses in the range 
$M_{\mathrm{ZAMS}} = 11.2 - 75 \, \Msol$. The set contains simulations using the
 two numerical codes and six different equations of state. Details can be found in
 \citep{Torres:2019a}. The reason to use one dimensional simulations for the model set
 is that the computational cost of those is significantly smaller than the cost of multidimensional
 simulations, so is easier to accumulate the statistics necessary to build a good model for $r(f)$.}

@@

{For all the simulations,} we mapped the pre-collapse state of the stars to a spherical
coordinate system with $n_r = 400$ zones in radial direction
distributed logarithmically with a minimum grid width of
$(\Delta r)_{\mathrm{min}} = 400 \, \mathrm{m}$ and an outer radius of
$r_{\mathrm{max}} = 8.3 \times 10^{9} \, \mathrm{cm}$ and
$n_{\theta} = 128$ equidistant cells in angular direction. For the
neutrino energies, we used a logarithmic grid with $n_e = 10$ bins up
to $240 \, \mathrm{MeV}$.

>>>>

{For the {\it model set}, we use the $25$ spherically symmetric (1D) simulations of \citep{Torres:2019a}
including progenitors with zero-age main sequence (ZAMS) masses in the range 
$M_{\mathrm{ZAMS}} = 11.2 - 75 \, \Msol$. The set contains simulations using the
 two numerical codes and six different equations of state. Details can be found in
 \citep{Torres:2019a}. The reason to use one dimensional simulations for the model set
 is that the computational cost of those is significantly smaller than the cost of multidimensional
 simulations, so is easier to accumulate the statistics necessary to build a good model for $r(f)$.}
 \pcd{For each time of each simulation we compute the ratio $r$ and the frequency of the $^2g_2$ mode by means of the linear analysis
 described in \cite{Torres:2018,Torres:2019a,Torres:2019b}. }

@@

{For all the simulations,} we mapped the pre-collapse state of the stars to a spherical
coordinate system with $n_r = 400$ zones in radial direction
distributed logarithmically with a minimum grid width of
$(\Delta r)_{\mathrm{min}} = 400 \, \mathrm{m}$ and an outer radius of
$r_{\mathrm{max}} = 8.3 \times 10^{9} \, \mathrm{cm}$ and
$n_{\theta} = 128$ equidistant cells in angular direction. For the
neutrino energies, we used a logarithmic grid with $n_e = 10$ bins up
to $240 \, \mathrm{MeV}$.
\pcd{Unlike the model set, the simulations in the test set cannot be 1D becase we need to 
extract the gravitational wave signal, which is a multi-dimensional effect. For each simulation
we extract the gravitational wave signal, $h_+(t)$,  by means of the quadrupole formula and compute the 
time evolution of the surface gravity, $r(t)$.}
